Summer 2024 Report

### 2025-01-24 Relations/Report.tex
Further work on tables

\begin{dfn}
  An element $a \in A$ is \emph{$R$-strongly recurrent} ($SR_R$) if every reduction sequence starting from $a$ reaches a recurrent element in a finite number of reductions.

@@

\begin{table}[h!]
  \centering
  \caption{Local implications}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, WR  & CR, SR  &   &   &   \\
  \hline
  \textbf{RP} & CR, WR  & CR, SR  &   &   &   \\
  \hline
  \textbf{NP} & NP, WR  & CR, WN  &   &   &   \\
  \hline
  \textbf{UN} & UN, WR  & UN, WN  &   &   &   \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Local implications - Counterexamples}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, CE-9  & CR, CE-6  & WIP , CE-9  &   &   \\
  \hline
  \textbf{RP} & CR, CE-9  & CR, CE-6  & WIP , CE-9 &   &   \\
  \hline
  \textbf{NP} & CE-10, CE-9  & CR, CE-6  & CE-11 , CE-9 &   &   \\
  \hline
  \textbf{UN} & CE-3, CE-9  & CE-3, CE-6  & CE-3, CE-9  &   &   \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table} 
\sacomment{We can potentially merge the two tables. Is it the case that we never move one step up the hierarchy? Is it always a case that if we move one step we move up all the steps, if that is the case then we just need to either express the relevant counterexample, or express the property attained.}

@@

  \item $\forall$ (R : $\mathscr{R}$ A) $\to$ $\forall$ is R -WN x $\to$ is R -UN x $\to$ is R -CR x
  \item $WN_R$ and $UN_R$ $\implies$ $CR_R$
  \item (Local) WR and UN $\implies$ NP 
  \item (Local) WN and UN $\implies$ SR

@@

    \end{center}
Counterexample to:
\begin{itemize}
  \item WN $\implies$ SN
  \item WN and CR $\implies$ SN
  \item WN, CR, and bounded $\implies$ SN
  \item WN, UN, and bounded $implies$ SN
  \item (Local) WN and UN $\implies$ SR
  \item (Local) WN and NP $\implies$ SR
  \item (Local) WN and RP $\implies$ SR
  \item (Local) WN and CR $\implies$ SR
\end{itemize}

@@

\end{center}
Counterexample to:
\begin{itemize}
  \item (Local) WR and UN $\implies$ WN 
  \item (Local) SR and UN $\implies$ WN 
  \item (Local) SR and NP $\implies$ WN 
  \item (Local) SR and RP $\implies$ WN 
  \item (Local) SR and CR $\implies$ WN 
\end{itemize}

@@

Counterexample to:
\begin{itemize}
  \item (Local) WR and NP $\implies$ RP 
\end{itemize}

>>>>

\begin{dfn}
  An element $a \in A$ is \emph{$R$-strongly recurrent} ($SR_R$) if every reduction sequence starting from $a$ reaches a recurrent element in a finite number of steps.

@@

In the following table red text indicates that classical properties are required for the implication to hold. Blue indicates we are currently unsure.

\begin{table}[h!]
  \centering
  \caption{Local implications}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, CE-9  & CR, CE-6  & CR , CE-9  & CR, CE-6  & CR , SN \\
  \hline
  \textbf{RP} & CR, CE-9  & CR, CE-6  & \red{CR} , CE-9 & CR, CE-6   & \red{CR} , SN \\
  \hline
  \textbf{WNFP} & CE-10, CE-9  & CR, CE-6  & CE-11 , CE-9 & CR, CE-6   & \red{CR} , SN \\
  \hline
  \textbf{UN} & CE-3, CE-9  & CE-3, CE-6  & CE-3, CE-9  & CE-3, CE-3  & \red{CR} , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Local implications - WCR }
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, CE-9  & CR, \blue{CE-6}  & CR , \blue{CE-9}  & CR, \blue{CE-6}  & CR , SN \\
  \hline
  \textbf{RP} & CR, CE-9  & CR, \blue{CE-6}  & \red{CR} , \blue{CE-9} & CR, \blue{CE-6}   & \red{CR} , SN \\
  \hline
  \textbf{WNFP} & CE-10, CE-9  & CR, \blue{CE-6}  & \blue{CE-11} , \blue{CE-9} & CR, \blue{CE-6}   & \red{CR} , SN \\
  \hline
  \textbf{UN} & CE-3, CE-9  & \blue{CE-3}, \blue{CE-6}  & \blue{CE-3}, \blue{CE-9}  & \blue{CE-3}, \blue{CE-3}  & \red{CR} , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Global implications}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, \blue{CE-9}  & CR, \blue{CE-6}  & CR , \blue{CE-9}  & CR, \blue{CE-6}  & CR , SN \\
  \hline
  \textbf{RP} & CR, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR} , \blue{CE-9} & CR, \blue{CE-6}   & \blue{CR} , SN \\
  \hline
  \textbf{WNFP} & \blue{CE-10}, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR} , \blue{CE-9} & CR, \blue{CE-6}   & \blue{CR} , SN \\
  \hline
  \textbf{UN} & \blue{CE-3}, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR}, \blue{CE-9}  & \blue{CE-3}, \blue{CE-3}  & \blue{CR} , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

\begin{table}[h!]
  \centering
  \caption{Global implications - WCR}
  \begin{tabular}{|l|c|c|c|c|c|}     
  \hline
  \textbf{CR} & CR, \blue{CE-9}  & CR, \blue{CE-6}  & CR , \blue{CE-9}  & CR, \blue{CE-6}  & CR , SN \\
  \hline
  \textbf{RP} & CR, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR} , \blue{CE-9} & CR, \blue{CE-6}   & CR , SN \\
  \hline
  \textbf{WNFP} & \blue{CE-10}, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR} , \blue{CE-9} & CR, \blue{CE-6}   & CR , SN \\
  \hline
  \textbf{UN} & \blue{CE-3}, \blue{CE-9}  & CR, \blue{CE-6}  & \red{CR}, \blue{CE-9}  & \blue{CE-3}, \blue{CE-3}  & CR , SN \\
  \hline
  & \textbf{WR} & \textbf{WN} & \textbf{SR} & \textbf{WN}$\boldsymbol{\land}$\textbf{SR} & \textbf{SN} \\
  \hline  
  \end{tabular}
\end{table}

@@

  \item $\forall$ (R : $\mathscr{R}$ A) $\to$ $\forall$ is R -WN x $\to$ is R -UN x $\to$ is R -CR x
  \item $WN_R$ and $UN_R$ $\implies$ $CR_R$
  \item (Local) WCR, WR and UN $\implies$ NP 
  \item (Local) WCR, WN and UN $\implies$ SR

@@

    \end{center}
Counterexample to:
\begin{itemize}
  \item WN $\implies$ SN
  \item WN and CR $\implies$ SN
  \item WN, CR, and bounded $\implies$ SN
  \item WN, UN, and bounded $implies$ SN
  \item (Local) WN and UN $\implies$ SR
  \item (Local) WN and NP $\implies$ SR
  \item (Local) WN and RP $\implies$ SR
  \item (Local) WN and CR $\implies$ SR
  \item (Local) WN, SR, and NP $\implies$ SN
  \item (Local) WN, SR, and RP $\implies$ SN
  \item (Local) WN, SR, and CR $\implies$ SN
\end{itemize}

@@

\end{center}
Counterexample to:
\begin{itemize}
  \item (Local) WCR, WR, and UN $\implies$ WN 
  \item (Local) SR and CR $\implies$ WN 
\end{itemize}

@@

Counterexample to:
\begin{itemize}
  \item (Local) WCR, WR, and NP $\implies$ RP 
\end{itemize}
